Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-13 paper/related_work.tex
More explicit FP comparison in related work.

Between expert systems and online games sit Mojo and \textit{Dojo}, by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces for error correction. Dojo extends this to distributed proofreading via a minimalistic web-based user interface. The authors define requirements for general proofreading tools, and then evaluate the accuracy and speed of Raveler, Mojo, and Dojo through a quantitative user study (Sec. 3 and 4)~\cite{haehn_dojo_2014}. In this paper, we use the Dojo system as a baseline for interactive proofreading and extend the experiment reported by Haehn \etal, where Raveler, Mojo, and Dojo are compared in terms of accuracy and speed.

@@

%Most relevant methods here use heuristics to analyze the image data to find potential errors. 
\textbf{Computer-aided Proofreading.} Plaza proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}, which finds split errors by analyzing segment size ratios across slices, then offers a yes/no choice to the user to correct these errors. Plaza reports that additional processing beyond FP is required to find merge errors. This method is open source and is integrated into Raveler. We use FP as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}).

A similar approach by Karimov \etal, known as guided volume editing~\cite{karimov_guided_volume_editing}, measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This was designed to let expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors generate possible boundaries using watershed, which inspired our merge error approach (Sec.~\ref{sec:methods}).

While focused proofreading and guided volume editing both use heuristics to analyze image data, Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user. Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets. Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.

>>>>

Between expert systems and online games sit Mojo and \textit{Dojo}, by Haehn \etal~\cite{haehn_dojo_2014,Neuroblocks}, which use simple scribble interfaces for error correction. Dojo extends this to distributed proofreading via a minimalistic web-based user interface. The authors define requirements for general proofreading tools, and then evaluate the accuracy and speed of Raveler, Mojo, and Dojo through a quantitative user study (Sec. 3 and 4)~\cite{haehn_dojo_2014}. Dojo had the highest performance. In this paper, we use Dojo as a baseline for interactive proofreading, and so we extend the Haehn \etal experiment.

@@

%Most relevant methods here use heuristics to analyze the image data to find potential errors. 
\textbf{Computer-aided Proofreading.} Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user. While it works on isotropic volumes, more work is needed to apply it to anisotropic volumes, like most connectomics datasets.

%Their method requires further work to overcome the requirement of isotropic volumes, a property not given for most connectomics datasets. Our approach, guided proofreading, works on isotropic as well as anisotropic data, and finds merge and split errors.

Karimov \etal propose guided volume editing~\cite{karimov_guided_volume_editing}, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors generate possible boundaries using watershed, which inspired our merge error approach (Sec.~\ref{sec:methods}).

Most closely related to our approach is the work of Plaza, who proposed \textit{focused proofreading} (FP) ~\cite{focused_proofreading}. FP finds split errors by analyzing segment size ratios across slices, then offers a yes/no choice to the user to correct these errors. Plaza reports that additional processing beyond FP is required to find merge errors. This method builds upon NeuroProof \cite{neuroproof2013} as its agglomerator, and is open source with integrated into Raveler. As the closest related work, we wish to use FP as a baseline to evaluate our approach (Sec.~\ref{sec:evaluation}). However, as Haehn \etal showed that Raveler is less performant than Dojo for novice users, we separate the backend split suggestions from the expert-level front end, and present our own interface (Sec.~\ref{sec:evaluation}).
